Titulo

### 2014-11-13 RotacionOutFlows/Paper/ms.tex
more things

\documentclass{emulateapj}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
\newcommand{\lya}{{Ly-$\alpha$~}}
\newcommand{\ang}{{$\theta_{gal}$~}}
\newcommand{\lognh}{{$\log{nH}$~}}
\newcommand{\vel}{{$v_{out}$~}}

@@

\keywords{Lyman Alpha Emission,  } 
\begin{abstract}
Here goes the abstract....
\end{abstract}

@@

\section{Theoretical Frame}
\label{sec:theo}
In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent \lya profile.\\

@@

The effect of the \lognh is the creation of 2 peaks: the left one very thin, tall and pronounced, and the right one very wide, small and soften. When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing ther height ratio until the left peak completely dissapears. The resulting spectrum, with high column density, is a wide single mountain with intensity significantly less than at the beginning. Fig. \ref{fig:influence_lognH} helps visualize this effect in a better way.\\

@@

\bibliographystyle{apj}
\begin{thebibliography}{38}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{CLARA}
{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666

\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
  {Maselli}}]{Verhamme06}
{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397

\bibitem[{P\'erez \& Granger(2007)}]{IPython}
P\'erez, F., \& Granger, B.~E. 2007, Computing in Science and Engineering, 9, 21

\end{thebibliography}

@@

%\section{Ejemplos para tener en cuenta}
%\label{sec:implementation}
%
%Ejemplo de ecuacion
%  
%\begin{equation}
%    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
%\end{equation}
%
%Ejemplo referencia a figura
%
%In Fig. \ref{fig:geometry} se ve .....
%
%Ejemplo cita 
%
%Scape of  at line center, which has also been associated with escape of ionizing (LyC) photons
%\citep{Behrens2014,2014arXiv1404.2958V}
% 
%Ejemplo display math
%
%\begin{displaymath}
%J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
%    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
%      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)},
%\end{displaymath} 
%
%Ejemplo tabla
%
%\begin{table}
%\begin{center}
%\begin{tabular}{c cccccc}
%\hline \hline
%Source & $\tau_{H}$ & &  $\ V_{\rm max}$& & \\
%Distribution& &    & (\kms) & & \\ 
%& & 0 & 100 &200 & 300\\ \hline 
%Homogeneous & $10^{5}$& 0.263 &  0.263 &  0.263 &  0.263  \\
%            & $10^{6}$ & 0.291 &   0.292 &  0.293 &  0.293 \\
%Central & $10^{5}$ &  0.096 & 0.096 &  0.096 & 0.096 \\
%  		&$10^{6}$ & 0.066 &  0.066 &  0.066 &  0.066 \\
%\hline
%\end{tabular}
%\caption{
% Ejemplo de tabla. } 
%\label{table:escape}
%\end{center}
%\end{table}

>>>>

%Document Class
\documentclass{latex/emulateapj}

%Packages and Commands
\include{latex/packages_commands}

@@

\keywords{Lyman Alpha Emission,  ....MISSING....}

\begin{abstract}
\noindent ------------------------------------------------------------------------------------------------------------------------------------\\
MISSING: The abstract\\
------------------------------------------------------------------------------------------------------------------------------------\\
\end{abstract}

@@

\section{Theoretical Background}
\label{sec:theo}
In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent \lya profile.\\

@@

The effect of the \lognh is the creation of 2 peaks: the left one very thin, tall and pronounced, and the right one very wide, small and soften. When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing their height ratio until the left peak completely dissapears. The resulting spectrum, with high column density, is a wide single mountain with intensity significantly less than at the beginning. Fig. \ref{fig:influence_lognH} helps visualize this effect in a better way.\\

@@

\bibliographystyle{latex/mn2e}
\bibliography{references}

@@

%\section{Ejemplos para tener en cuenta}
%\label{sec:implementation}
%
%Ejemplo de ecuacion
%  
%\begin{equation}
%    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
%\end{equation}
%
%Ejemplo referencia a figura
%
%In Fig. \ref{fig:geometry} se ve .....
% 
%Ejemplo display math
%
%\begin{displaymath}
%J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
%    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
%      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)},
%\end{displaymath} 
%
%Ejemplo tabla
%
%\begin{table}
%\begin{center}
%\begin{tabular}{c cccccc}
%\hline \hline
%Source & $\tau_{H}$ & &  $\ V_{\rm max}$& & \\
%Distribution& &    & (\kms) & & \\ 
%& & 0 & 100 &200 & 300\\ \hline 
%Homogeneous & $10^{5}$& 0.263 &  0.263 &  0.263 &  0.263  \\
%            & $10^{6}$ & 0.291 &   0.292 &  0.293 &  0.293 \\
%Central & $10^{5}$ &  0.096 & 0.096 &  0.096 & 0.096 \\
%  		&$10^{6}$ & 0.066 &  0.066 &  0.066 &  0.066 \\
%\hline
%\end{tabular}
%\caption{
% Ejemplo de tabla. } 
%\label{table:escape}
%\end{center}
%\end{table}
